Fast processing of JUNGFRAU data with the Alpaka library

### 2020-03-02 Publication/manuscript.tex
Updated Manuscript.pdf

\textcolor{magenta}{
expected: up to 1000 Frames/s; 100 to 1000 Frames per stream \\
\textbf{comparison of devices (expected):}
\begin{itemize}
	\item after 10 Frames per stream the frame count has diminishing effects on performance (on GPU)
	\item on CPU: number of Frames per streams doesn't effect performance much
	\item photon calculation a lot faster (\textasciitilde4x) than energy; clustering in between (this effect will probably be less on CPU)
	\item number and type of kernels mostly insignificant for GPU; some effects on CPU
	\item frame summing will speed up almost linearly on less frames on GPU, on CPU not so big differences
	\item almost linear scaling with number of GPUs
	\item almost linear scaling with number of cores on CPU
	\item pedestal updates and masking doesn't effect performance mush
	\item exception: clustering (mainly on GPU): scales linearly with clusters to download \ calculate
	\item multiple modules show weak scaling
	\item effects of cluster size???
\end{itemize}
}

@@

\textcolor{magenta}{
more backends to come (SYCL, ...)
}

>>>>

\textcolor{magenta}{
expected: up to 1000 Frames/s; 100 to 1000 Frames per stream \\
\textbf{comparison of devices (expected):}
\begin{itemize}
	\item after 10 Frames per stream the frame count has diminishing effects on performance (on GPU)
	\item on CPU: number of Frames per streams doesn't effect performance much
	\item photon calculation a lot faster (\textasciitilde4x) than energy; clustering in between (this effect will probably be less on CPU)
	\item number and type of kernels mostly insignificant for GPU; some effects on CPU
	\item frame summing will speed up almost linearly on less frames on GPU, on CPU not so big differences
	\item almost linear scaling with number of GPUs
	\item almost linear scaling with number of cores on CPU
	\item pedestal updates and masking doesn't effect performance much
	\item exception: clustering (mainly on GPU): scales linearly with clusters to download \ calculate
	\item multiple modules show weak scaling until bandwidth limit is reached
	\item effects of cluster size???
\end{itemize}
}

@@

\textcolor{magenta}{
more backends to come (SYCL, ...) \\
AMD GPU support in light of Frontier HPC construction
}
